\bf Model Visualization Techniques for a Social Network Model

### 2017-08-30 paper.Rnw

<<tableofmeans>>=
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
senM1est <- read.csv("data/congress/senateM1ests.csv")
senM2est <- read.csv("data/congress/senateM2ests.csv")
senM3est <- read.csv("data/congress/senateM3ests.csv")
senM1est$Model <- "M1"
senM2est$Model <- "M2"
senM3est$Model <- "M3"
senM1est$Sim <- 1:nrow(senM1est)
senM2est$Sim <- 1:nrow(senM2est)
senM3est$Sim <- 1:nrow(senM3est)
senM1est %>% gather(parameter, estimate, Rate:recip) %>% select(Sim, Model, parameter, estimate) -> senM1est2 
senM2est %>% gather(parameter, estimate, Rate:jumpXTransTrip) %>% select(Sim, Model, parameter, estimate) -> senM2est2 
senM3est %>% gather(parameter, estimate, Rate:nbrDist2twice) %>% select(Sim, Model, parameter, estimate) -> senM3est2 
senateEsts <- rbind(senM1est2, senM2est2, senM3est2)
senateEsts$parameter <- as.factor(senateEsts$parameter)
levels(senateEsts$parameter) <- c("beta1", "beta3", "beta4", "alpha1", "alpha2", "alpha3", "beta2")
SSE <-
  senateEsts %>% group_by(Model, parameter) %>% 
  summarize(meanEst = mean(estimate), sdEst = sd(estimate)) %>% 
  mutate(val = paste0(sprintf("%.3f",meanEst), " ", "(", sprintf("%.3f", sdEst), ")")) %>% 
  select(Model, parameter, val) %>% 
  spread(Model, val) %>% arrange(as.character(parameter))
SFE <- simu2 %>% group_by(Model, parameter) %>% 
  summarize(meanEst = mean(estimate), sdEst = sd(estimate)) %>% 
   mutate(val = paste0(sprintf("%.3f",meanEst), " ", "(", sprintf("%.3f", sdEst), ")")) %>% 
  select(Model, parameter, val) %>% 
  spread(Model, val) %>% arrange(parameter)
@

>>>>

<<tableofmeans>>=
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
senM1est <- read.csv("data/congress/senateM1ests.csv")
senM2est <- read.csv("data/congress/senateM2ests.csv")
senM3est <- read.csv("data/congress/senateM3ests.csv")
senM1est$Model <- "M1"
senM2est$Model <- "M2"
senM3est$Model <- "M3"
senM1est$Sim <- 1:nrow(senM1est)
senM2est$Sim <- 1:nrow(senM2est)
senM3est$Sim <- 1:nrow(senM3est)
senM1est %>% gather(parameter, estimate, Rate:recip) %>% dplyr::select(Sim, Model, parameter, estimate) -> senM1est2 
senM2est %>% gather(parameter, estimate, Rate:jumpXTransTrip) %>% dplyr::select(Sim, Model, parameter, estimate) -> senM2est2 
senM3est %>% gather(parameter, estimate, Rate:nbrDist2twice) %>% dplyr::select(Sim, Model, parameter, estimate) -> senM3est2 
senateEsts <- rbind(senM1est2, senM2est2, senM3est2)
senateEsts$parameter <- as.factor(senateEsts$parameter)
levels(senateEsts$parameter) <- c("beta1", "beta3", "beta4", "alpha1", "alpha2", "alpha3", "beta2")
SSE <-
  senateEsts %>% group_by(Model, parameter) %>% 
  summarize(meanEst = mean(estimate), sdEst = sd(estimate)) %>% 
  mutate(val = paste0(sprintf("%.3f",meanEst), " ", "(", sprintf("%.3f", sdEst), ")")) %>% 
  dplyr::select(Model, parameter, val) %>% 
  spread(Model, val) %>% arrange(as.character(parameter))
SFE <- simu2 %>% group_by(Model, parameter) %>% 
  summarize(meanEst = mean(estimate), sdEst = sd(estimate)) %>% 
   mutate(val = paste0(sprintf("%.3f",meanEst), " ", "(", sprintf("%.3f", sdEst), ")")) %>% 
  select(Model, parameter, val) %>% 
  dplyr::select(Model, parameter, val) %>% 
  spread(Model, val) %>% arrange(parameter)
@
